---
title: "Webscrapping data with mapscrapper"
output: github_document
author: Vincent Pellissier
---
## Preliminary steps
### Installing a usable web browser

Before we can actually scrap data from the website, we need to setup a web browser that will run in the background. I recommand using Chrome (mainly because I could not manage doing it with Firefox but you're free to try it).

### Installing Rtools

We also needs an external software to create some external files, called RTools. The installer can be downloaded [here](https://cran.r-project.org/bin/windows/Rtools/index.html). During the instalation tick the box "Add Rtools to system path"

### Installing the mapscrapper package

A brand new, not super efficient and certainly not optimized package to scrap the opentransportmap website!

``` {r eval = F}
devtools::install_github("vpellissier/mapscrapper", ref = "pipes")
```

### Installing and starting a Selenium server
There is several ways to do this, but here we are going to use a standalone server.
THe server can be downloaded from the [Selenium Project](http://selenium-release.storage.googleapis.com/index.html).
Once downloaded, the server can be started using command line (either windows + cmd, or Tools/Shell from RStudio):

`> java  -jar path/file_name`

Where path is the path were you have downloaded the file, and file the name of the file (should end with a .jar extension)


## Scrapping the website
Downloading all the zip file for a given country is quite straightforward.
First, we need to know the name of the countries in the first dropdownlist

### Gathering the names of the countries (NUTS0)
The dropdown_values function can list all the possible values of a given NUTS level (here, 0):

```{r}
library(mapscrapper, quietly = T)
names_nuts0 <- dropdown_values(nuts = 0, remDr = NULL)
```
If this return an error message, you need to re-run the previous line of code!

The function returns a vector containing the names of the NUTS0 as they are in the website:
```{r echo = F}
head(names_nuts0)
```

### Downloading the maps for a given country
The zip files are going to be downloaded in a folder with the name of the country inside the root path (if it does not exist, the folder will be created):
```{r eval = F}
download_map_country("Estonia", root_path = "C:/Maps")
```

